Redshift Evolution of the Underlying Type Ia Supernova Stretch Distribution

### 2020-04-23 Nicolas.tex
Back to latest. Comms included, seem to be ok except mean bias in orange

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Article_figures/BBC_-stretchevol_grouped.pdf}
    \caption{Difference of mean stretch standardization (in mag, using
        $\alpha=0.156$ from \citealt{scolnic2018a}) between the per-sample
        Gaussian asymmetric modeling and our Base drifting model, as a function
        of redshift, considering the SDSS, PS1 and SNLS datasets. The colored
        markers show the difference for SDSS, PS1 and SNLS samples (see legend)
        considering the individual SN redshifts (no redshift cut applied). The
        orange markers represent their mean evolution in 30 regularly-spaced
        redshift bins. This must be multiplied by the amplitude of the Malmquist
        bias correction to derive the SN distance modulus bias affecting
        cosmology, see text.}
    \label{fig:magdrift}
\end{figure}

@@

\bibliographystyle{aa} % style aa.bst
\begin{thebibliography}{} 
% A
%\bibitem[Abbott et al.(2018)]{abbott2018} Abbott, T.~M.~C., Abdalla, F.~B., Alarcon, A., et al.\ 2018, \prd, 98, 043526

@@

%\bibitem[Ata et al.(2017)]{ata2017} Ata, M., Kitaura, F.-S., Chuang, C.-H., et al.\ 2017, \mnras, 467, 3993

@@

% B
\bibitem[Bazin et al.(2011)]{bazin2011} Bazin, G., Ruhlmann-Kleider, V., Palanque-Delabrouille, N., et al.\ 2011, \aap, 534, A43

@@

% C
\bibitem[Campbell et al.(2013)]{campbell2013} Campbell, H., D'Andrea, C.~B., Nichol, R.~C., et al.\ 2013, \apj, 763, 88

%\bibitem[Chabanier et al.(2019)]{chabanier2019} Chabanier, S., Millea, M., \& Palanque-Delabrouille, N.\ 2019, \mnras, 489, 2247

@@

%\bibitem[Coles, \& Jones(1991)]{coles1991} Coles, P., \& Jones, B.\ 1991, \mnras, 248, 1

%\bibitem[Conley et al.(2011)]{conley2011} Conley, A., Guy, J., Sullivan, M., et al.\ 2011, \apjs, 192, 1

% D
\bibitem[D'Andrea et al.(2011)]{dandrea2011} D'Andrea, C.~B., Gupta, R.~R., Sako, M., et al.\ 2011, \apj, 743, 172

@@

% E
% F
\bibitem[Feeney et al.(2019)]{feeney2019} Feeney, S.~M., Peiris, H.~V., Williamson, A.~R., et al.\ 2019, \prl, 122, 061105

@@

% G
\bibitem[Graham et al.(2019)]{graham2019} Graham, M.~J., Kulkarni, S.~R., Bellm, E.~C., et al.\ 2019, \pasp, 131, 078001

@@

%\bibitem[Guy et al.(2010)]{guy2010} Guy, J., Sullivan, M., Conley, A., et al.\ 2010, \aap, 523, A7

%\bibitem[Graziani et al.(2019)]{graziani2019} Graziani, R., Courtois, H.~M., Lavaux, G., et al.\ 2019, \mnras, 488, 5438

% H
\bibitem[Hamuy et al.(1996)]{hamuy1996} Hamuy, M., Phillips, M.~M., Suntzeff, N.~B., et al.\ 1996, \aj, 112, 2391

@@

%\bibitem[Howell et al.(2009)]{howell2009} Howell, D.~A., Sullivan, M., Brown, E.~F., et al.\ 2009, \apj, 691, 661

% I
\bibitem[Ivezi{\'c} et al.(2019)]{lsstpaper} Ivezi{\'c}, {\v{Z}}., Kahn, S.~M., Tyson, J.~A., et al.\ 2019, \apj, 873, 111

% J
\bibitem[Jones et al.(2015)]{jones2015} Jones, D.~O., Riess, A.~G., \& Scolnic, D.~M.\ 2015, \apj, 812, 3
1

@@

% K
\bibitem[Kelly et al.(2010)]{kelly2010} Kelly, P.~L., Hicken, M., Burke, D.~L., et al.\ 2010, \apj, 715, 743

@@

% L
\bibitem[Lampeitl et al.(2010)]{lampeitl2010} Lampeitl, H., Smith, M., Nichol, R.~C., et al.\ 2010, \apj, 722, 566

% M
\bibitem[Mannucci et al.(2005)]{mannucci2005} Mannucci, F.,
  Della Valle, M., Panagia, N., et al.\ 2005, \aap, 433, 807 
\bibitem[Mannucci et al.(2006)]{mannucci2006} Mannucci, F.,
  Della Valle, M., \& Panagia, N.\ 2006, \mnras, 370, 773

@@

% N
\bibitem[Neill et al.(2006)]{neill2006} Neill, J.~D., Sullivan, M., Balam, D., et al.\ 2006, \aj, 132, 1126

@@

% O
% P
\bibitem[Pan et al.(2014)]{pan2014} Pan, Y.-C., Sullivan, M., Maguire, K., et al.\ 2014, \mnras, 438, 1391

@@

%\bibitem[Planck Collaboration et al.(2016)]{planck2016} Planck Collaboration, Ade, P.~A.~R., Aghanim, N., et al.\ 2016, \aap, 594, A13

@@

% Q
% R
\bibitem[Reid et al.(2019)]{reid2019} Reid, M.~J., Pesce, D.~W., \& Riess, A.~G.\ 2019, arXiv e-prints, arXiv:1908.05625

@@

% S
\bibitem[Sako et al.(2008)]{sako2008} Sako, M., Bassett, B., Becker, A., et al.\ 2008, \aj, 135, 348

@@

%\bibitem[Scolnic et al.(2018)]{scolnic2018b} Scolnic, D.~M., Lochner, M., Gris, P., et al.\ 2018, arXiv e-prints, arXiv:1812.00516

@@

% T
\bibitem[Tasca et al.(2015)]{tasca2015} Tasca, L.~A.~M., Le F{\`e}vre, O., Hathi, N.~P., et al.\ 2015, \aap, 581, A54

% U 
% V
% W
\bibitem[Wiseman et al.(2020)]{wiseman2020} Wiseman, P., Smith, M., Childress, M., et al.\ 2020, arXiv e-prints, arXiv:2001.02640

@@

% X
% Y

% Z
\end{thebibliography}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%
%
%  BACKUP 
%
%%%%%%%%%%%%%%%%%%%%%%%%

%For clarity with the next models, we named it 3G2M2S$_{\text{SNf}}$ for it has a total of 3 Gaussians but with only 2 means and 2 standard deviations, and has been fitted on SNf data only.

%We implemented and compared 10 models in total, 4 of which have an
%evolution with the redshift from $\delta(z)$, and 6 don't ($\delta(z) = f =\mathrm{cst}$). The ones with and evolution are:
\begin{itemize}
    \item 3G2M2S, the one we described (but fitted on all the data);
    \item 3G2M1S, where this time $\sigma_1 \equiv \sigma_2$;
    \item 2G2M2S, model taken from HOWELL 2009 where we added $\delta(z)$;
    \item 3G3M3S, with three independent Gaussians.
\end{itemize}
The ones without a stretch evolution are the same ones but with an ``F'' implying
we set $\delta(z) = f = \mathrm{cst}$, and two others:
\begin{itemize}
    \item 1G1M1S, where there is no distinction between old and young SNe;
    \item 1G1M2S, taken from KESLLER 2017 and used in recent cosmological
        analysis SCOLNIC 2018. It's an asymetric model where
\end{itemize}
\begin{align}
 p(x_1^i, \mathrm{d} x_1^i | \mu, \sigma_-, \sigma_+) = 
    \begin{cases}
        \mathcal{N} \left(\mu, \sqrt{\sigma_-{}^2 + \mathrm{d} x_1^i{}^{2}}\right) (x_1^i) & \text{if
        } x_1^i\geq \mu\\
        \mathcal{N} \left(\mu, \sqrt{\sigma_+{}^2 + \mathrm{d} x_1^i{}^{2}}\right) (x_1^i), &
        \text{else}
    \end{cases}
\end{align}

The fitted parameters are shown in Table~\ref{tab:val}.

\begin{table*}[htbp!]
    \centering
    \caption{Values of the best-it parameters for all the models. In red are the non-coherent ones which coincides with the models without an evolution of the fraction of young SNe Ia with the redshift.}
    \label{tab:val}
    \begin{tabular}{c c c c c c c}\hline\hline

        Model & $a$ & $f$ & $\mu_1$ & $\sigma_1$ & $\mu_2$ &
        $\sigma_2$ \\\hline

        3G2M2S$_{\mathrm{SNf}}$ & $0.48 \pm 0.07$ & none & $0.39 \pm 0.07$ &
        $0.56 \pm 0.05$ & $-1.5 \pm 0.1$ & $0.52 \pm 0.09$ \\

        3G2M2S & $0.48 \pm 0.17$ & none & $0.36 \pm 0.08$ & $0.61 \pm 0.05$ &
        $-1.3 \pm 0.2$ & $0.60 \pm 0.12$ \\

        3G2M2SF & \textcolor{red}{$0.1 \pm 0.6$} & \textcolor{red}{$0.2 \pm
        0.6$} & $-0.9 \pm 0.7$ & $0.7 \pm 0.3$ & $0.5 \pm 0.2$ & $0.6 \pm 0.1$
        \\

        3G2M1S & $0.47 \pm 0.07$ & none & $0.35 \pm 0.04$ & $0.61 \pm 0.03$ &
        $-1.25 \pm 0.10$ & $\sigma_1$ \\

        3G2M1SF & \textcolor{red}{$0.2 \pm 0.9$} & $0.7 \pm 0.3$ & $0.36 \pm
        0.04$ & $0.60 \pm 0.03$ & $-1.23 \pm 0.10$ & $\sigma_1$ \\

        2G2M2S & none & none & $0.49 \pm 0.04$ & $0.54 \pm 0.03$ & $-0.72 \pm
        0.08$ & $0.83 \pm 0.07$ \\

        2G2M2SF & none & $0.3 \pm 0.2$ & $-0.9 \pm 0.6$ & $0.7 \pm 0.2$ & $0.5
        \pm 0.2$ & $0.56 \pm 0.09$ \\\hline

    \end{tabular} \bigbreak

\begin{tabular}{c c c}\hline\hline

    Model & $\mu$ & $\sigma$ \\\hline

    1G1M1S & $0.01 \pm 0.04$ & $0.90 \pm 0.03$ \\\hline

\end{tabular} \bigbreak

\begin{tabular}{c c c c c}\hline\hline

    Model & $\mu$ & $\sigma_-$ & $\sigma_+$ \\\hline

    1G1M2S & $0.16617 \pm 0.00004$ & $1.07 \pm 0.04$ & $0.69 \pm 0.03$ \\\hline

\end{tabular} \bigbreak

\begin{tabular}{c c c c c c c c c}\hline\hline

    Model & $a$ & $f$ & $\mu_1$ & $\sigma_1$ & $\mu_2$ & $\sigma_2$ &
    $\mu_3$ & $\sigma_3$ \\\hline

    3G3M3S & $0.14 \pm 0.08$ & none & $0.51 \pm 0.06$ & $0.54 \pm 0.04$ & $-1.9
    \pm 0.2$ & $0.29 \pm 0.11$ & $-0.55 \pm 0.12$ & $0.67 \pm 0.15$ \\

    3G3M3SF & $0.2 \pm 0.2 $ & $0.10 \pm 0.04 $ & $-1.7 \pm 0.2$ & $0.4 \pm 0.1$
            & $0.9 \pm 0.1$ & $0.3 \pm 0.2$ & $0.0 \pm 0.2$ & $0.7 \pm 0.1$
            \\\hline

\end{tabular} \bigbreak
\end{table*}

To test the coherence of this model, we also fitted it using all the data from
the surveys indistinctly. These results are shown Fig.~\ref{fig:model_all}.

\begin{table*}
    \centering
    \caption{BBC comparison}
    \label{tab:bbc_comp}
    \begin{tabular}{c c |c c c |c c c |c c c}\hline\hline\\[-1.05em]
     &  & \multicolumn{3}{|c}{Asym (this)} & \multicolumn{3}{|c}{Asym (SK18/S18)} & \multicolumn{3}{|c}{Base SNf} \\
    N$_{\mathrm{SN}}$ & Survey & $\mathcal{X}^2$ & AIC & Free param & $\mathcal{X}^2$ & AIC & Free param & $\mathcal{X}^2$ & AIC & Free param \\\hline
    167 & SDSS & 445.0 & 451.2 & 3 & 457.9 & 464.0 & 3 & 452.9 & 452.9 & 0\\
    160 & PS1 & 397.4 & 403.6 & 3 & 397.6 & 403.7 & 3 & 405.2 & 405.2 & 0\\
    102 & SNLS & 252.7 & 259.0 & 3 & 254.5 & 260.8 & 3 & 269.5 & 269.5 & 0\\
    114 & SNf & 299.3 & 305.5 & 3 & -- & -- & -- & 268.6 & 279.1 & 5\\
    543 & Total & 1394.5 & 1419.1 & 12 & -- & -- & -- & 1396.0 & 1406.2 & 5\\
    429 & Total-SNf & 1095.2 & 1113.6 & 9 & 1110.0 & 1128.4 & 9 & 1127.5 & 1127.5 & 0\\\hline\hline
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{BBC comparison}
    \label{tab:bbc_comp}
    \begin{tabular}{c |c c c |c c c}\hline\hline\\[-1.05em]
     & \multicolumn{3}{|c}{Asym (this)}  & \multicolumn{3}{|c}{Base SNf} \\
    Survey & $\mathcal{X}^2$ & AIC & Free param & $\mathcal{X}^2$ & AIC & Free param \\\hline
    SNf & 299.3 & 305.5 & 3 & 268.6 & 279.1 & 5\\
    SDSS & 445.0 & 451.2 & 3 & 452.9 & 452.9 & 0\\
    PS1 & 397.4 & 403.6 & 3 & 405.2 & 405.2 & 0\\
    SNLS & 252.7 & 259.0 & 3  & 269.5 & 269.5 & 0\\
    Total & 1394.5 & 1419.1 & 12 & 1396.0 & 1406.2 & 5\\\hline\hline
    \end{tabular}
\end{table*}we are also testing non-drifting models by restricting the ``Base'' and ``Howell'' models to use a supposedly redshift-independent fraction $\delta(z) = f$ of young SNe; these models are labeled ``Base constant'' and ``Howell constant''.} \yc{\uline{fix labels!!! \nn{done}}}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Article_figures/BBC_-stretchevol_grouped.pdf}
    \caption{Difference of mean stretch standardization (in mag, using
        $\alpha=0.156$ from \citealt{scolnic2018a}) between the per-sample
        Gaussian asymmetric modeling and our Base drifting model, as a function
        of redshift, considering the SDSS, PS1 and SNLS datasets. The colored
        markers show the difference for SDSS, PS1 and SNLS samples (see legend)
        considering the individual SN redshifts (no redshift cut applied). The
        orange markers represent their mean evolution in 30 regularly-spaced
        redshift bins. This must be multiplied by the amplitude of the Malmquist
        bias correction to derive the SN distance modulus bias affecting
        cosmology, see text. \nn{\textit{Apparently, there is some issue with
        the mean of all surveys combined. See Greg's comments.}}}
    \label{fig:magdrift}
\end{figure}

@@

\bibliographystyle{aa} % style aa.bst
\begin{thebibliography}{} 
% A

%\bibitem[Abbott et al.(2018)]{abbott2018} Abbott, T.~M.~C., Abdalla, F.~B.,
%Alarcon, A., et al.\ 2018, \prd, 98, 043526

@@

%\bibitem[Ata et al.(2017)]{ata2017} Ata, M., Kitaura, F.-S., Chuang, C.-H., et
%al.\ 2017, \mnras, 467, 3993

@@

% B

\bibitem[Bazin et al.(2011)]{bazin2011} Bazin, G., Ruhlmann-Kleider, V.,
Palanque-Delabrouille, N., et al.\ 2011, \aap, 534, A43

@@

% C

\bibitem[Campbell et al.(2013)]{campbell2013} Campbell, H., D'Andrea, C.~B.,
Nichol, R.~C., et al.\ 2013, \apj, 763, 88

%\bibitem[Chabanier et al.(2019)]{chabanier2019} Chabanier, S., Millea, M., \&
%Palanque-Delabrouille, N.\ 2019, \mnras, 489, 2247

@@

%\bibitem[Coles, \& Jones(1991)]{coles1991} Coles, P., \& Jones, B.\ 1991,
%\mnras, 248, 1

%\bibitem[Conley et al.(2011)]{conley2011} Conley, A., Guy, J., Sullivan, M., et
%al.\ 2011, \apjs, 192, 1

% D

\bibitem[D'Andrea et al.(2011)]{dandrea2011} D'Andrea, C.~B., Gupta, R.~R.,
Sako, M., et al.\ 2011, \apj, 743, 172

@@

% E
% F

\bibitem[Feeney et al.(2019)]{feeney2019} Feeney, S.~M., Peiris, H.~V.,
Williamson, A.~R., et al.\ 2019, \prl, 122, 061105

@@

% G

\bibitem[Graham et al.(2019)]{graham2019} Graham, M.~J., Kulkarni, S.~R., Bellm,
E.~C., et al.\ 2019, \pasp, 131, 078001

@@

%\bibitem[Guy et al.(2010)]{guy2010} Guy, J., Sullivan, M., Conley, A., et al.\
%2010, \aap, 523, A7

%\bibitem[Graziani et al.(2019)]{graziani2019} Graziani, R., Courtois, H.~M.,
%Lavaux, G., et al.\ 2019, \mnras, 488, 5438

% H

\bibitem[Hamuy et al.(1996)]{hamuy1996} Hamuy, M., Phillips, M.~M., Suntzeff,
N.~B., et al.\ 1996, \aj, 112, 2391

@@

%\bibitem[Howell et al.(2009)]{howell2009} Howell, D.~A., Sullivan, M., Brown,
%E.~F., et al.\ 2009, \apj, 691, 661

% I

\bibitem[Ivezi{\'c} et al.(2019)]{lsstpaper} Ivezi{\'c}, {\v{Z}}., Kahn, S.~M.,
Tyson, J.~A., et al.\ 2019, \apj, 873, 111

% J

\bibitem[Jones et al.(2015)]{jones2015} Jones, D.~O., Riess, A.~G., \& Scolnic,
D.~M.\ 2015, \apj, 812, 3 1

@@

% K

\bibitem[Kelly et al.(2010)]{kelly2010} Kelly, P.~L., Hicken, M., Burke, D.~L.,
et al.\ 2010, \apj, 715, 743

@@

% L

\bibitem[Lampeitl et al.(2010)]{lampeitl2010} Lampeitl, H., Smith, M., Nichol,
R.~C., et al.\ 2010, \apj, 722, 566

% M

\bibitem[Mannucci et al.(2005)]{mannucci2005} Mannucci, F., Della Valle, M.,
Panagia, N., et al.\ 2005, \aap, 433, 807

\bibitem[Mannucci et al.(2006)]{mannucci2006} Mannucci, F., Della Valle, M., \&
Panagia, N.\ 2006, \mnras, 370, 773

@@

% N

\bibitem[Neill et al.(2006)]{neill2006} Neill, J.~D., Sullivan, M., Balam, D.,
et al.\ 2006, \aj, 132, 1126

@@

% O
% P

\bibitem[Pan et al.(2014)]{pan2014} Pan, Y.-C., Sullivan, M., Maguire, K., et
al.\ 2014, \mnras, 438, 1391

@@

%\bibitem[Planck Collaboration et al.(2016)]{planck2016} Planck Collaboration,
%Ade, P.~A.~R., Aghanim, N., et al.\ 2016, \aap, 594, A13

@@

% Q
% R

\bibitem[Reid et al.(2019)]{reid2019} Reid, M.~J., Pesce, D.~W., \& Riess,
A.~G.\ 2019, arXiv e-prints, arXiv:1908.05625

@@

% S

\bibitem[Sako et al.(2008)]{sako2008} Sako, M., Bassett, B., Becker, A., et al.\
2008, \aj, 135, 348

@@

%\bibitem[Scolnic et al.(2018)]{scolnic2018b} Scolnic, D.~M., Lochner, M., Gris,
%P., et al.\ 2018, arXiv e-prints, arXiv:1812.00516

@@

% T

\bibitem[Tasca et al.(2015)]{tasca2015} Tasca, L.~A.~M., Le F{\`e}vre, O.,
Hathi, N.~P., et al.\ 2015, \aap, 581, A54

% U 
% V
% W

\bibitem[Wiseman et al.(2020)]{wiseman2020} Wiseman, P., Smith, M., Childress,
M., et al.\ 2020, arXiv e-prints, arXiv:2001.02640

@@

% X
% Y
% Z
\end{thebibliography}
\end{document}
